Gravitational-wave sensitivity curves

### 2014-07-02 Detectors.tex
changed refs to Appendix A

\subsection{Ground based detectors}\label{sec:ground}
On Earth approximations to the free floating test masses described above are achieved by suspending the mass from a pendulum system with natural frequency much greater than that of the GW. The interferometric detectors listed in Table \ref{table:t} are all sensitive to GWs in the frequency range ${\cal{O}}(10-10^{3})\,\textrm{Hz}$. They all have multiple narrow lines in their sensitivity curves, which arise from noise sources in the instrument including resonances in the suspension system and electronic noise at multiples of $60\,\textrm{Hz}$: these have been removed in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega} for clarity. The detectors fall broadly into three categories: 1\textsuperscript{st} generation detectors, which have already operated; 2\textsuperscript{nd} generation detectors currently under construction; and 3\textsuperscript{rd} generation detectors at the planning stage.

@@

The sensitivity bandwidth of a PTA is set by the sampling properties of the data set. If measurements are spaced in time by $\delta t$ and taken for a total length of time $T$ then the PTA is sensitive to frequencies in the range $(1/T)<f<(1/\delta t)$. The characteristic strain that the PTA is sensitive to scales linearly with $f$ in this range. This gives the wedge shaped curves plotted in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega}. The absolute value of the sensitivity is fixed by normalising to a calculated limit at a given frequency for each PTA. For a discussion of the sensitivities of PTA to both individual sources and stochastic background see \cite{MooreTaylorGair}.

@@

\subsubsection{SKA}
The sensitivity curve plotted in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega} for the SKA (Square Kilometer Array) assume a values of $\delta t^{2}_{\textrm{r.m.s.}}$ a factor of 10 better than current PTAs and 20 pulsars timed for twice as long as the current EPTA.

>>>>

\subsection{Ground based detectors}\label{sec:ground}
On Earth approximations to the free floating test masses described above are achieved by suspending the mass from a pendulum system with natural frequency much greater than that of the GW. The interferometric detectors listed in Table \ref{table:t} are all sensitive to GWs in the frequency range ${\cal{O}}(10-10^{3})\,\textrm{Hz}$. They all have multiple narrow lines in their sensitivity curves, which arise from noise sources in the instrument including resonances in the suspension system and electronic noise at multiples of $60\,\textrm{Hz}$: these have been removed in the \ref{app:a} figures for clarity. The detectors fall broadly into three categories: 1\textsuperscript{st} generation detectors, which have already operated; 2\textsuperscript{nd} generation detectors currently under construction; and 3\textsuperscript{rd} generation detectors at the planning stage.

@@

The sensitivity bandwidth of a PTA is set by the sampling properties of the data set. If measurements are spaced in time by $\delta t$ and taken for a total length of time $T$ then the PTA is sensitive to frequencies in the range $(1/T)<f<(1/\delta t)$. The characteristic strain that the PTA is sensitive to scales linearly with $f$ in this range. This gives the wedge shaped curves plotted in \ref{app:a}. The absolute value of the sensitivity is fixed by normalising to a calculated limit at a given frequency for each PTA. For a discussion of the sensitivities of PTA to both individual sources and stochastic background see \cite{MooreTaylorGair}.

@@

\subsubsection{SKA}
The sensitivity curves plotted in \ref{app:a} for the SKA (Square Kilometer Array) assume values of $\delta t^{2}_{\textrm{r.m.s.}}$ a factor of 10 better than current PTAs and 20 pulsars timed for twice as long as the current EPTA.
